How did local health infrastructure and socio-political factors within different states and counties in the United States affect the disparities in COVID-19 outcomes, and what lessons can be learned for more targeted public health preparedness and response strategies in future pandemics?

### 2024-02-10 outputs/paper/paper.qmd
updated paper

@@

ggplot(data = world_ghs) +
  geom_sf(aes(fill = `OVERALL SCORE`), color = "white") +
  scale_fill_distiller(palette = "Spectral", na.value = "lightgrey", 
                       name = "GHS Index Score", direction = 1,
                       limits = c(min(ghs_data$`OVERALL SCORE`, na.rm = TRUE), max(ghs_data$`OVERALL SCORE`, na.rm = TRUE)),
                       labels = comma) +  # Use comma to format numbers with commas
  labs(title = "Global Health Security Index Scores by Country") +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5))

>>>>

`R` [@citeR] was the language and environment used for the bulk of this analysis, alongside `tidyverse` [@citeTidyVerse], `sf` [@citeSF], `readxl` [@citeReadXL], `knitr` [@citeKnitR], `janitor` [@citeJanitor], `lubridate` [@citeLubridate], `dplyr` [@citeDplyr], `data.table` [@citeDataTable], `RColorBrewer` [@citeRColorBrewer], `ggpubr` [@citeggpubr], `ggplot2` [@citeggplot], `here` [@citeHere], and `scales` [@citeScales].

@@

ggplot(data = world_ghs) +
  geom_sf(aes(fill = `OVERALL SCORE`), color = "white") +
  scale_fill_distiller(palette = "Spectral", na.value = "lightgrey", 
                       name = "GHS Index Score", direction = 1,
                       limits = c(min(ghs_data$`OVERALL SCORE`, na.rm = TRUE), max(ghs_data$`OVERALL SCORE`, na.rm = TRUE)),
                       labels = comma) +  # Use comma to format numbers with commas
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5))
